PAGAI : a path sensitive static analyser

### 2012-05-18 papers/TAPAS2012/pagai.tex

Abstract domains are provided by the APRON library
\citep{DBLP:conf/cav/JeannetM09}, and include convex polyhedra (from the builtin
Polka ``PK'' library), octagons, intervals, and linear congruences. It also has
an interface with the Parma Polyhedra Library (CITATION!!), giving access to
more abstract domains.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}
through their C API, and can also operate with any SMT-solver supporting the
SMT-Lib 2 standard \cite{BarST-SMTLIB} through a pipe.

>>>>

Abstract domains are provided by the APRON library
\citep{DBLP:conf/cav/JeannetM09}, and include convex polyhedra (from the builtin
Polka ``PK'' library), octagons, intervals, and linear congruences. It also has
an interface with the Parma Polyhedra Library (CITATION!!), giving access to
more abstract domains.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}
through their C API, and can also operate with any SMT-solver supporting the
SMT-Lib 2 standard \cite{BarST-SMTLIB,BarST-SMT-10} through a pipe.
